Index measures for oak decline severity using phenotypic descriptors

### 2020-08-12 manuscript/manuscript.Rmd
fixed table formatting

```{r site-information}
readd(site_information) %>%
  kable(format = 'latex',
        booktabs = TRUE,
        caption = 'Overview of the surveyed site information.') %>%
  column_spec(3,width = '4cm') %>%
  column_spec(4,width = '3cm')
```

@@

PDI_lime_analysis_table %>%
  kable(format = 'latex',
        booktabs = TRUE,
        escape = FALSE,
        caption = 'LIME results for oak decline severity cases in the PDI index model $M_{PDI}$. Top four important descriptors show. Descriptors ordered by descending absolute weight within each case.') %>%
  collapse_rows(columns = 1:3, latex_hline = "major", valign = "middle")
```

@@

DAI_lime_analysis_table %>%
  kable(format = 'latex',
        booktabs = TRUE,
        escape = FALSE,
        caption = 'LIME results of oak decline type and severity in the DAI index model $M_{DAI}$. Top four important descriptors shown. Descriptors ordered by descending absolute weight within each case.') %>%
  column_spec(5,width = '4cm') %>%
  collapse_rows(columns = 1:4, latex_hline = "custom", valign = "middle",custom_latex_hline = 1:4)
```

>>>>

```{r site-information}
readd(site_information) %>%
  kable(format = 'latex',
        booktabs = TRUE,
        caption = 'Overview of the surveyed site information.') %>%
  column_spec(3,width = '4cm') %>%
  column_spec(4,width = '3cm') %>%
  column_spec(5,width = '2cm') %>%
  column_spec(6,width = '2cm')
```

@@

PDI_lime_analysis_table %>%
  kable(format = 'latex',
        booktabs = TRUE,
        escape = FALSE,
        caption = 'LIME results for oak decline severity cases in the PDI index model $M_{PDI}$. Top four important descriptors show. Descriptors ordered by descending absolute weight within each case.') %>%
  column_spec(1,width = '2cm') %>%
  column_spec(3,width = '2cm') %>%
  collapse_rows(columns = 1:3, latex_hline = "major", valign = "middle")
```

@@

DAI_lime_analysis_table %>%
  kable(format = 'latex',
        booktabs = TRUE,
        escape = FALSE,
        caption = 'LIME results of oak decline type and severity in the DAI index model $M_{DAI}$. Top four important descriptors shown. Descriptors ordered by descending absolute weight within each case.') %>%
  column_spec(1,width = '1.5cm') %>%
  column_spec(2,width = '1.5cm') %>%
  column_spec(4,width = '2cm') %>%
  column_spec(5,width = '3.5cm') %>%
  column_spec(6,width = '3cm') %>%
  collapse_rows(columns = 1:4, latex_hline = "custom", valign = "middle",custom_latex_hline = 1:4)
```
